\section{\methodname: An Effective RL Recipe for Code Localization}

This section presents the methodology used to train \methodname, covering training data curation and environment construction (\S\ref{sec:data_creation}), the agent scaffold (\S\ref{sec:agent_scaffold}), reward design (\S\ref{sec:reward_design}), and the RL training setup (\S\ref{sec:train_algo}). Figure~\ref{fig:system_diagram} provides an overview of our approach.

\subsection{Data and Environment Curation}
\label{sec:data_creation}
We describe our approach to curating data and constructing RL environments for training \methodname. Given a GitHub issue $\mathcal{I}$ in a Python repository $\mathcal{R}$, we process the ground-truth issue resolution patch $\mathcal{P}$ to extract the localization targets at three granularities. Specifically, we define the ground-truth target as $y^{\star} = (F^{\star}, M^{\star}, U^{\star})$, where $F^{\star} = {f_1^{\star}, \dots, f_{N_f}^{\star}}$ is the set of modified files, $M^{\star} = {m_1^{\star}, \dots, m_{N_m}^{\star}}$ is the set of modified modules, and $U^{\star} = {u_1^{\star}, \dots, u_{N_u}^{\star}}$ is the set of functions or methods edited by the patch $\mathcal{P}$. An example of these targets is illustrated in Figure~\ref{fig:system_diagram}. The LLM agent is tasked with predicting $y^{\star}$ given the issue description $\mathcal{I}$ and the pre-PR repository state $\mathcal{R}$. We extract ground truth by using patch-processing scripts from LocAgent~\citep{chen-etal-2025-locagent} and enhance them to (i) detect additions of member functions and class attributes at the module and file level, (ii) capture modifications to import statements and global variables at the file level, and (iii) ignore edits to docstrings within functions and classes.

We curate training instances by processing GitHub issues collected by prior work~\citep{yang2025swesmithscalingdatasoftware, pan2025trainingsoftwareengineeringagents}, originally intended for training agents to resolve issues. We discard issues with empty descriptions and whose PRs create or delete files, as the agent cannot predict the name of newly created files and we cannot determine ground-truth modules or functions for deleted files. We ignore non-Python files (e.g., \texttt{README.md}) because function- and module-level information cannot be extracted from them.

We construct the RL environment by cloning the pre-PR commit of the repository to a specific path known to the agent via its prompt. Since localization does not require execution of repository code, we do not install project dependencies or use sandboxes. Notably, as our agent only requires a terminal, environment setup overhead is significantly lower than prior work whose scaffolds require code graphs, vector databases, or dependency parsers.
\input{Figures/system_diagram}
\subsection{OpenHands-Bash: Our Agent Scaffold}\label{sec:agent_scaffold}

We use OpenHands Agent SDK~\citep{wang2025openhandssoftwareagentsdk} to implement our agent as it performs strongly across software engineering benchmarks, implements core tools (e.g., terminal), supports parallel tool-calling, and has a modular design that easily integrates with our training backend. The agent is equipped with a \texttt{Terminal} tool that supports standard Unix commands (e.g., \texttt{find}, \texttt{ls}, \texttt{sed}). We install \texttt{ripgrep}~\citep{ripgrep} in the agent's environment, which is a command-line utility for fast grep-style search using regex patterns recursively through all code files in a directory. Furthermore, the agent uses the \texttt{LocalizationFinish} tool to submit predictions. We refer to this scaffold as \textbf{OpenHands-Bash}.

Our initial experiments used a string-based output format from \citet{chen-etal-2025-locagent}, but we found training with this format is sensitive to noisy reward signals due to brittle validation and parsing. We address this by requiring the agent to terminate via the \texttt{LocalizationFinish} tool, enforcing a structured output schema and simplifying parsing, improving reward fidelity. Appendix~\ref{appendix:prompts} includes detailed prompts and tool definitions for our agent.

\subsection{Reward Design}\label{sec:reward_design}
For each trajectory $\tau$ sampled from the LLM agent, we extract the predicted localization output $y = (F, M, G)$ from the \texttt{LocalizationFinish} tool, which specifies the predicted files, modules, and functions. Given the ground-truth location $y^{\star} = (F^{\star}, M^{\star}, G^{\star})$, we compute F1 scores at each granularity. Concretely, for each set $S \in \{F, M, G\}$ with the corresponding ground truth $S^{\star} \in \{F^{\star}, M^{\star}, G^{\star}\}$, we compute the F1 score (i.e. the harmonic mean of precision and recall): $r^{\mathsf{F1-file}}$, $r^{\mathsf{F1-module}}$, and $r^{\mathsf{F1-func}}$. Our reward function is defined as:
\begin{equation}
\begin{aligned}
    r(\tau, y, y^{\star}) &= r^{\mathsf{F1-file}}(y, y^{\star}) + r^{\mathsf{F1-module}}(y, y^{\star}) + r^{\mathsf{F1-func}}(y, y^{\star})
\end{aligned}
\label{eqn:reward}
\end{equation}
In early experiments for \methodname-14B, we observed training collapse characterized by near-zero rewards in later stages. Our analysis indicated that the agent frequently exhausted the step budget without submitting predictions. To mitigate this, we use an auxiliary binary reward $r^{\mathsf{turn}}(\tau, k)$ that assigns 1 if and only if the agent terminates in exactly $k$ turns, where $k$ is the step limit. This simple mechanism encourages timely termination within the step limit. Accordingly, the final reward for \methodname-14B adds this binary term to $r(\tau, y, y^{\star})$ in Equation~\ref{eqn:reward}. We also explored auxiliary rewards to incentivize parallel tool-calling, motivated by ~\citet{cognition2025swegrep}, but found these interventions to hurt overall performance. Thus, we instead explicitly prompt the agent to use parallel tool-calling (Appendix~\ref{appendix:prompts}).

\subsection{RL Training Algorithm}\label{sec:train_algo}

We implement our training backend using SkyRL~\citep{griggs2025skrylv01}, a modular framework for LLM reinforcement learning. SkyRL supports asynchronous RL~\citep{fu2026areallargescaleasynchronousreinforcement}, improving GPU utilization by parallelizing rollout generation and weight optimization. Parameter updates are triggered after collecting a sufficient number of rollouts potentially sampled from slightly stale checkpoints. Concretely, trajectories used in the $n^{\text{th}}$ training step may be sampled from checkpoints that are atmost $t$ steps stale, where $t$ is the maximum staleness (set to 4 in our experiments). After each optimization step, we synchronize updated weights with the vLLM~\citep{kwon2023efficient} engines and terminate any incomplete inference requests.

We train models using Group Sequence Policy Optimization (GSPO)~\citep{zheng2025groupsequencepolicyoptimization}. The loss function is expressed below where $\theta$ denotes model parameters; $i$ indexes sequences in a group of size $G$; $y_i$ is the $i^{th}$ output sequence with length $|y_i|$, and $y_{i,t}$ is its $t^{th}$ token. $\pi_\theta$ and $\pi_{\theta_{\text{old}}}$ are current and older policies, $\hat{A}_i$ is the advantage, and $\varepsilon$ is the clipping parameter:
{
\small % or \footnotesize
\begin{align}
    \mathcal{J}_{\text{GSPO}}(\theta) &= 
    \mathbb{E}_i \left[ \frac{1}{G} \sum_{i=1}^{G} \min\left( s_i(\theta) \hat{A}_i,\, \text{clip}\left( s_i(\theta), 1-\varepsilon, 1+\varepsilon \right) \hat{A}_i \right) \right]
    \label{eq:gspo}
\end{align}
}
where,  $s_i$ is the importance ratio derived from sequence likelihood~\citep{zheng-etal-2023-click}:
\begin{align}
    s_i(\theta) = \exp\left( \frac{1}{|y_i|} \sum_{t=1}^{|y_i|} \log \frac{\pi_\theta(y_{i,t} | x, y_{i,<t})}{\pi_{\theta_{\text{old}}}(y_{i,t} | x, y_{i,<t})} \right)
    \label{eq:is}
\end{align}
Following Dr. GRPO~\citep{liu2025understandingr1zeroliketrainingcritical}, we remove the KL regularization term from the loss and the standard deviation from the advantage calculation.
\begin{align}
    \hat{A}_i = r_i - \text{mean}(\mathbf{r}), \mathbf{r} = \{r_1, ..., r_G\}
\end{align}
We also disable entropy loss and mask loss for rollouts that exhaust maximum steps without submitting predictions. Appendix~\ref{appendix:rl_ablation_study} includes additional analysis on the effect of the RL algorithm on localization performance.