\section{Analysis}
This section presents detailed analysis on the benefits of effective localization on issue resolution (\S\ref{sec:downstream_swebench}) and the evolving tool-use behaviors during RL (\S\ref{sec:tool_use_behaviour}).

\subsection{Does Effective Code Localization Improve Issue Resolution?}\label{sec:downstream_swebench}
\input{Figures/heatmap_14B}
% \input{Tables/downstream_swebench_performance}
We show that augmenting OpenHands issue resolution agent~\citep{wang2025openhandssoftwareagentsdk} with relevant code retrieved by \methodname improves performance on SWE-Bench Verified. We consider three settings: (1) a vanilla baseline without localization, (2) augmenting the agent with locations retrieved by \methodname-14B, and (3) augmenting the agent with oracle locations parsed from the gold patch (\S\ref{sec:data_creation}). 
For (2) and (3), the user prompt is modified to include the names of localized files, modules, and functions (Appendix~\ref{appendix:prompts_swe_bench}). 

We evaluate Qwen3-4B-Instruct-2507 and Qwen3-Coder-30B-A3B-Instruct compare the performance of the three settings using issue resolution rate, and their efficiency using instance-level averages of the number of steps per trajectory and the total input and output tokens accumulated across all turns. Table~\ref{tab:downstream_swe_bench} presents the detailed results.
\begin{wraptable}{r}{0.5\columnwidth}
    \centering
    % \vspace{-15pt} % Adjust vertical alignment as needed
    \resizebox{0.5\columnwidth}{!}{%
        \renewcommand{\arraystretch}{1.1}
        \begin{tabular}{lcccc}
        \toprule
        \makecell[l]{\textbf{Localization }\\\textbf{Approach}} & \makecell{\textbf{Resolution}\\\textbf{Rate $\uparrow$}} & \makecell{\textbf{Avg. \# }\\\textbf{Steps $\downarrow$}} & \makecell{\textbf{Avg. Input}\\\textbf{Tokens $\downarrow$}} & \makecell{\textbf{Avg. Output}\\\textbf{Tokens $\downarrow$}} \\
        \midrule
        \rowcolor{blue!15!white}\multicolumn{5}{c}{\textbf{Qwen3-4B-Instruct}} \\
        \midrule
        None (Vanilla) & 13.40\% & \underline{16.09} & 344.37K & \underline{2.98K} \\
        \methodname-14B & \underline{17.20\%} & \textbf{13.91} & \textbf{284.26K} & \textbf{2.78K} \\
        Oracle & \textbf{19.60\%} & 16.41 & \underline{327.75K} & 3.17K \\
        \midrule
        \rowcolor{pink!40!white}\multicolumn{5}{c}{\textbf{Qwen3-Coder-30B-A3B-Instruct}} \\
        \midrule
        None (Vanilla) & 45.20\% & 51.00 & 1596.71K & 13.49K \\
        \methodname-14B & \underline{46.00\%} & \underline{48.11} & \underline{1511.53K} & \underline{13.22K} \\
        Oracle & \textbf{52.00\%} & \textbf{46.74} & \textbf{1358.60K} & \textbf{12.48K} \\
        \bottomrule
        \end{tabular}%
    }
    \caption{Issue resolution performance on SWE-Bench Verified: augmenting the agent with relevant locations improves performance and efficiency. Best metric is \textbf{bold-faced} and 2$^{nd}$ best is \underline{underlined}.}
    \label{tab:downstream_swe_bench}
    \vspace{-15pt}
\end{wraptable}

For Qwen3-4B-Instruct, augmenting the agent with locations retrieved by \methodname-14B increases the resolution rate by \textbf{3.8\%}, while reducing trajectory length by \textbf{2.18} steps, and input and output tokens by \textbf{17.46\%} and \textbf{6.71\%} respectively. Similar efficiency gains are observed for Qwen3-Coder-30B-A3B-Instruct, with \textbf{2.89} fewer steps and \textbf{5.33\%} fewer input tokens and \textbf{2.00\%} fewer output tokens, while achieving comparable performance with a small improvement (+0.80\%). For both LLMs, replacing \methodname predictions with oracle locations yields further performance gains (\textbf{+6.00\%} for 30B and \textbf{+2.40\%} for 4B). The 30B model also benefits with improved efficiency, with \textbf{1.37} fewer steps and reductions of \textbf{10.12\%} and \textbf{5.60\%} in input and output tokens. Overall, these results indicate that continued improvements in code localization will further enhance both the performance and efficiency of issue resolution agents.

\subsection{How does the tool-use behaviour of \methodname evolve during RL?}\label{sec:tool_use_behaviour}
To analyze the evolving tool-use behaviors RL, we plot the distribution of Unix utilities invoked by the LLM in Figure~\ref{fig:merged_tool_use}. We parse rollouts sampled from model checkpoints at every 10 training steps. Command usage is aggregated across these checkpoints to identify the top-8 frequently used commands. For each checkpoint, we compute the relative usage frequency of each utility for all rollouts logged in that training step.

We observe convergence in tool usage during RL. While the 14B LLM initially invokes various utilities, after around 200 training steps it uses \emph{only} on two commands: \texttt{ripgrep} (\texttt{rg}) and \texttt{sed}. Similarly, while the 4B LLM initially uses a many utilities, it converges to mainly using \texttt{ripgrep}, \texttt{sed}, \texttt{cat}, \texttt{find} and \texttt{xargs}. Appendix~\ref{appendix:traj_examples} presents example trajectories for 4B and 14B LLMs. Thus, effective localization can be done with an even simpler agent using a small subset of Unix utilities without requiring access to the entire Unix terminal which is crucial in security-sensitive deployments.
% We provided analysis of evolving tool-use behaviours of \methodname-4B and \methodname-14B during their respective RL training runs. For all training steps, we parse the Unix utilities from the raw commands issued by the agent when using the \texttt{Terminal} tool across all turns in each sampled rollout. We restrict our analysis to the top-8 Unix utilities based on their total usage frequency across over the entire training run. Finally, we plot the heatmap of the relative usage frequencies of these utilities for every 10 training steps, 

% In Figure \ref{fig:merged_tool_use}, we observe that at the start of training, \methodname tries out multiple different bash commands such as \texttt{cat}, \texttt{grep}, etc. However, as training progresses, the agent quickly converges to using less command variations and after 250 steps only uses \texttt{rg} and \texttt{sed}. This is most likely due to the \texttt{rg} command being comprehensive enough as functionalities from \texttt{cat}, \texttt{find}, and \texttt{grep} can be done with \texttt{rg}. \texttt{cd} also sees dimishing use likely due to the the more effective use of \texttt{rg} that makes changing directory unnecessary.