\input{ICML/Tables/baseline_comparison}
\section{An Overview of Code Localization}
\label{sec:background}
Issue resolution is one of the most prominent use cases of software engineering agents, involving the automatic resolution of GitHub issues in a code repository~\citep{chowdhury2024swebenchverified}. Given a natural language issue description, which may include code snippets and error logs to aid in bug resolution, coding agents must first navigate the pre-PR repository to identify relevant locations that require modification, and we refer to this process as \emph{code localization}.

Prior work on code localization has proposed specialized agent frameworks and trained open-source LLMs for this task. Table~\ref{tab:baseline_comparison} summarizes prior approaches and compares them with ours. A key limitation of existing methods is that their agent frameworks are restricted to a single programming language, typically Python, due to reliance on language-specific static analysis tools, like AST-based parsers. Extending these approaches to other languages, therefore, requires additional engineering effort. For example, LocAgent~\citep{chen-etal-2025-locagent} and OrcaLoca~\citep{yu2025orcalocallmagentframework} employ language-specific parsers to construct code graphs that capture hierarchical repository dependencies, requiring expensive pre-indexing. CoSIL~\citep{liu2025cosil} dynamically builds module-call graphs to capture ``import'' relationships and function-call graphs to capture ``invoke'' and ``inherit'' relationships. Furthermore, RepoSearcher~\citep{ma2025toolintegratedreinforcementlearningrepo} introduces specialized retrieval tools, for example to extract file imports or search for functions within classes. While CoSIL and RepoSearcher avoid pre-indexing, they still depend on language-specific static analysis to construct call graphs or implement special-purpose tools. Similarly, RepoNavigator~\citep{zhang2025one} provides a ``jump'' tool that resolves Python symbol definitions using a Python language server built using static analysis tools like AST and dependency graphs. In contrast, our approach, \methodname, leverages an agent scaffold that relies \emph{solely} on a standard bash terminal for code localization, which makes it inherently programming language-agnostic by design.

Unlike most prior methods, which either do not train LLMs using their proposed agent frameworks, such as CoSIL and OrcaLoca, or rely on supervised distillation from proprietary closed-source LLMs via rejection sampling fine-tuning~\citep{yuan2023scalingrelationshiplearningmathematical}, like LocAgent and RepoSearcher, \methodname post-trains LLMs directly with reinforcement learning, thereby eliminating dependence on expensive closed-source models for data curation.

Finally, \methodname has a \emph{significantly simpler} agent scaffold both in terms of both engineering overhead and tool count. Since the bash terminal is already a core component of standard coding agents like OpenHands~\citep{wang2025openhandssoftwareagentsdk}, SWE-Agent~\citep{yang2024sweagentagentcomputerinterfacesenable}, and Claude Code~\citep{anthropic_claude_code_2025}, our approach avoids the need to implement specialized task-specific tools or agent scaffolds, unlike prior work. Moreover, when measured by the size of the agent's action space, excluding any exit/finish tools, \methodname uses only 1 tool, compared to 3-5 tools in prior methods. Refer to Appendix~\ref{appendix:related_work_detailed} for a more comprehensive review of prior work.
% \gncomment{We need math here.}

% Software engineering tasks often involve solving GitHub issues in a code repository. These issues describe the underlying problem in natural language and may also include code snippets to reproduce the bug and related error logs. Agents for automated issue resolution need to identify relevant locations from the code repository before editing the codebase to fix the issue. This process of finding parts of repository is called code-localization and is regarded as an essential pre-requisite step for the issue resolution task. 

% Formally, given an issue description regarding a bug or question related to a repository $x \in \mathcal{X}$, the task of code localization is to predict a set of relevant items $y \subset \mathcal{U}$ where $\mathcal{U}$ represents all possible sets of items (file name, modules, functions, or specific code lines). Such a system would be trained to maximize the Dice coefficient based on the target set $\hat{y} \subset \mathcal{U}$, $\text{Dice}(y, \hat{y}) = \frac{2 |y \cap \hat{y}|}{|y| + |\hat{y}|}$.
% $y \sim f(x)$

% In fact, tasks such as SWE-Bench~\cite{jimenez2024swebenchlanguagemodelsresolve} have early variants where the code-localization part has already been "solved" by including the relevant files in the prompt.
% While various 
% Traditional information retrieval methods often rely on heuristics such as semantic similarity between keywords and context. Agentic code-search systems, on the other hand, enable more targeted repository exploration via tool use.

% In a code localization task, a system must return a set of relevant targets. These targets may have hierarchical attributes corresponding to the file, module/class, or function level (our work considers these three levels of granularity). Performance is measured using F1, which considers both precision and recall of the retrieval system.