\section{Analysis}
This section presents comprehensive analysis that offers more insights about the \methodname recipe. We discuss the advantages of effective code localization on downstream issue resolution (\S\ref{sec:downstream_swebench}) and analyze evolving tool-use behaviors during RL (\S\ref{sec:tool_use_behaviour}).

\subsection{Does Effective Code Localization Improve Issue Resolution?}\label{sec:downstream_swebench}
\input{ICML/Tables/downstream_swebench_performance}
\input{ICML/Figures/heatmap_14B}

We demonstrate that augmenting issue-resolution agents with code localized by \methodname improves both downstream performance and efficiency on SWE-Bench Verified when using the OpenHands Software Agent SDK~\citep{wang2025openhandssoftwareagentsdk}. We consider three settings: (1) a vanilla baseline without any localization, (2) augmenting the agent with locations retrieved by \methodname-14B, and (3) augmenting the agent with oracle locations parsed from the gold patch (\S\ref{sec:data_creation}). For settings (2) and (3), we modify the user prompt by including the names of localized files, modules, and functions (see Appendix~\ref{appendix:prompts_swe_bench}).

We perform experiments using two LLMs: Qwen3-4B-Instruct-2507 and Qwen3-Coder-30B-A3B-Instruct, using a 128K context-window, a maximum of 100 turns, and recommended decoding hyperparameters from Qwen3 developers. We compare these three approaches based on performance, using issue resolution rate (\% of issues successfully fixed), and efficiency, using instance-level averages of number of steps per trajectory, and total input and output tokens accumulated over all turns.

We present experimental results in Table \ref{tab:downstream_swe_bench}. For Qwen3-4B-Instruct-2507, improved localization quality leads to substantial gains in both performance and efficiency: augmenting the agent with locations retrieved by \methodname-14B increases the resolution rate by \textbf{3.80\%}, while using \textbf{2.18} steps fewer on average, and reducing input and output tokens by \textbf{17.46\%} and \textbf{6.71\%}, respectively. Similar trends are observed for Qwen3-Coder-30B-A3B-Instruct, where augmentation with \methodname-14B yields notable efficiency gains with \textbf{2.89} fewer steps on average and reductions of \textbf{5.33\%} and 2.00\% in input and output tokens, while achieving a slightly higher resolution rate (+0.80\%). For both models, replacing \methodname localization with oracle locations results in a further performance boost (\textbf{+6.00\%} for 30B and \textbf{+2.40\%} for 4B). The 30B model additionally benefits from improved efficiency, with \textbf{1.37} fewer steps and reductions of \textbf{10.12\%} and \textbf{5.60\%} in input and output tokens. Overall, these results indicate that continued improvements in code localization will likely further enhance both the performance and efficiency of issue resolution agents.

\subsection{How does the tool-use behaviour of \methodname evolve during RL?}\label{sec:tool_use_behaviour}

To analyze how the tool-use behavior of our 4B and 14B models evolves during RL training, we study the distribution of Unix utilities invoked for code localization. We use rollouts logged during training and parse calls to the \texttt{Terminal} tool to extract the executed Unix commands. For analysis, we consider rollouts collected from model checkpoints at every 10 training steps. Command usage is aggregated across these checkpoints to identify the top-8 most frequently used utilities. For each model checkpoint, we then compute the relative frequency with which these utilities are invoked across all rollouts logged for that training step. Figure~\ref{fig:merged_tool_use} presents how the relative distribution of these utilities evolves during training using heatmaps.

We observe a clear convergence in tool usage as training progresses. While the 14B model initially invokes a diverse set of utilities (e.g., \texttt{grep}, \texttt{find}, \texttt{wc}, and \texttt{cat}), after approximately 200 training steps it predominantly relies on only two commands: \texttt{ripgrep} (\texttt{rg}) and \texttt{sed}. A similar trend is observed for the 4B model, which initially explores a broader set of utilities but eventually converges to primarily using \texttt{ripgrep}, \texttt{sed}, \texttt{cat}, and \texttt{xargs}. Appendix~\ref{appendix:traj_examples} presents example trajectories illustrating how these utilities are used by models for code localization. These findings suggest that effective code localization can be achieved with a substantially simpler agent scaffold that exposes only a small subset of Unix utilities, indicating that access to the entire Unix command-line interface through the terminal may not be necessary, especially in security-sensitive deployments.
% We provided analysis of evolving tool-use behaviours of \methodname-4B and \methodname-14B during their respective RL training runs. For all training steps, we parse the Unix utilities from the raw commands issued by the agent when using the \texttt{Terminal} tool across all turns in each sampled rollout. We restrict our analysis to the top-8 Unix utilities based on their total usage frequency across over the entire training run. Finally, we plot the heatmap of the relative usage frequencies of these utilities for every 10 training steps, 

% In Figure \ref{fig:merged_tool_use}, we observe that at the start of training, \methodname tries out multiple different bash commands such as \texttt{cat}, \texttt{grep}, etc. However, as training progresses, the agent quickly converges to using less command variations and after 250 steps only uses \texttt{rg} and \texttt{sed}. This is most likely due to the \texttt{rg} command being comprehensive enough as functionalities from \texttt{cat}, \texttt{find}, and \texttt{grep} can be done with \texttt{rg}. \texttt{cd} also sees dimishing use likely due to the the more effective use of \texttt{rg} that makes changing directory unnecessary.