\section{Introduction}

Large language models have transformed automated software development, enabling systems to resolve real-world software engineering issues with increasing capability~\citep{jimenez2024swebenchlanguagemodelsresolve,chen2024masai}. A critical prerequisite for issue resolution is \textbf{code localization}---identifying the specific files, classes, and functions that require modification~\citep{xia2024agentless}. This task is particularly challenging in large repositories where relevant code may be scattered across hundreds of files with complex interdependencies. Recent analysis from production coding agents reveals that code search accounts for over 60\% of total time in agent trajectories~\citep{cognition2025swegrep,morph2025warpgrep}, with many retrieved code snippets being irrelevant, leading to \textbf{context rot}---the systematic degradation of model performance as input length increases~\citep{chroma2025contextrot}---and reduced effectiveness on long-horizon tasks.

To address this inefficiency, the community has begun exploring \textbf{specialized subagents} dedicated to code localization. Rather than relying on a single monolithic agent to perform both search and editing, this paradigm delegates localization to a lightweight subagent that rapidly identifies relevant code before handing off to an editing agent. Notable examples include SWE-grep from Cognition AI~\citep{cognition2025swegrep} which employs parallel tool calling to accelerate search, and WarpGrep from Morph Labs~\citep{morph2025warpgrep} which uses RL to train a context retrieval subagent. Additionally, AI companies have also recognized this challenge: Anthropic's Claude Code emphasizes efficient context gathering~\citep{anthropic2025claudecode}, and Cursor's semantic search improves agent code retention by 2.6\% on large codebases~\citep{cursor2025semsearch}.

Despite these advances, \textbf{most high-performing code localization systems remain closed-source}. SWE-grep and WarpGrep are proprietary while some open-source alternatives like LocAgent~\citep{Chen2025} rely on expensive frontier models such as Claude 3.5 Sonnet for trajectory distillation. Although RepoNavigator~\citep{zhang2025reponavigator} demonstrates RL training without distillation, our work differs in several key aspects. \tycomment{Please specify our key differences from RepoNavigator.} This creates barriers around \textbf{cost}, \textbf{reproducibility}, and \textbf{research accessibility}. The lack of open training recipes also limits our understanding of effective design choices for this task.

In this work, we present \textbf{an open-source recipe for training dedicated code localization agents using reinforcement learning}. Out contributions are three-fold:

\begin{enumerate}
    \item \textbf{Multi-level localization with RL training}: We adapt established benchmarks (SWE-Smith~\cite{yang2024sweagent} and SWE-Bench~\cite{jimenez2024swebenchlanguagemodelsresolve}) for code localization with ground-truth labels at three granularity levels (files, classes, functions). We train \methodname using GSPO with a multi-level F1 reward, directly from a pretrained open-source model (Qwen3-14B) without closed-source distillation.
    
    \item \textbf{Training stability techniques}: We identify and address training instabilities including format degradation, loss masking issues, and tool call errors. We introduce a custom finish tool and format reward that prevent training collapse. \lscomment{These techniques are empirically validated but may need ablation studies to quantify individual contributions.}
    
    \item \textbf{Competitive performance with full release}: 
    \lscomment{What does "full release" mean?}\methodname achieves competitive performance on SWE-Bench Lite ([TBD]\% File F1), Verified ([TBD]\% File F1), and Pro ([TBD]\% File F1), approaching LocAgent with Claude 3.5 Sonnet (77.33\% File F1 @1) while using only a 14B open-source model. \tycomment{Performance numbers to be filled in by core authors. Verify LocAgent baseline is 77.33\% @1.} We release training code, reward functions, model checkpoints, and evaluation datasets.
\end{enumerate}

Our work demonstrates that with careful reward design and training techniques, open-source models can achieve competitive code localization performance without relying on expensive proprietary models or closed-source distillation.