\section{Method}

In this section, we describe the method used for training \methodname - training data curation, design of our agent scaffold, reward function used during training, and the RL algorithm we use.

% We demonstrate an accessible method to produce a competitive code-search agent using open-source artifacts. We train a 14b and a 4b model with this method.

\subsection{Data and Environment Curation}
\label{sec:data_creation}

We now describe our methodology for curating our training data and developing the RL environment for our task. Given access to a GitHub issue $\mathcal{I}$ in the code repository $\mathcal{R}$, we process the ground-truth patch $\mathcal{P}$ that resolves this issue to extract ground-truth localization target $y^{*}$ at three levels of granularity: edited files, edited modules, and edited functions. The task of the LLM agent is to predict $y^{*}$, given the issue description $\mathcal{I}$ and the pre-PR code repository $\mathcal{R}$. Note that we utilize the patch processing scripts from LocAgent~\citep{chen-etal-2025-locagent}, which we adapt and extend to better suit our task setting as described below.

First, we filter out all pull requests from our training data that add or remove files as files added by a PR cannot be predicted, and we cannot determine relevant ground-truth modules and entities for deleted files. Second, we exclude all non-Python files (e.g., README.md) modified by the PR from the ground truth, as we cannot extract function- or module-level information from such files. Third, we discard instances with empty issue descriptions. Finally, we extend the original processing logic of \citet{chen-etal-2025-locagent} to correctly handle several important edit operations: detecting the addition of functions and class attributes at the module and file levels, capturing changes to imports and global variables at the file level, and ignoring edits to docstrings in functions and classes.

We prepare the environment for the agent by cloning the specific commit of the repository $\mathcal{R}$ in a specific location known to the agent. Since code localization does not require executing code from the repository, we do not  install any repository dependency nor apply any containerization. Unlike prior methods like LocAgent~\citep{chen-etal-2025-locagent}, our deliberate choice a simple agent scaffold \emph{significantly} simplifies setting up the environment for the agent as it does not require access to a code graph, dependency parser, vector database etc. \sonicomment{TODO: add concrete info here from baselines and explain why we have a simpler setup without graph/vector index, etc.}

% After preprocessing, the resulting dataset consists of 39K instances drawn from 131 different repositories
\sonicomment{I have shifted the SWE-Smith para to experimental setup}
 % We utilize the SWE-smith~\citep{yang2025swesmithscalingdatasoftware} dataset during training which consists of a total of 39K instances from 131 repositories after preprocessing and filtering.

\tycomment{Add a table with some statistics about the dataset}\sonicomment{ It is not top priority rn, if you have it ready, please add it to appendix and add a reference here pls.}

% \begin{table}
%     \centering
%     \missingfigure[\linewidth]{Training data statistics}
%     \caption{Statistics of training data}
%     \label{tab:training_data}
% \end{table}


\subsection{Agent Scaffold}\label{sec:agent_scaffold}

We use the OpenHands Software Agent SDK~\cite{wang2025openhandssoftwareagentsdk} as the agent scaffold for \methodname, given its strong performance on numerous software engineering benchmarks as a result of its modular design, robust implementation of various crucial tools (for e.g. terminal, file editor, etc.), and the ability to augment the scaffold with additional tools, and integrate the agent scaffold with our training backend.

% , given its well-designed  OpenHands  Software-Agent-SDK handles the processes such as constructing the complete system message that includes the tool description, multi-turn process along with stop-condition. 
In particular, the agent is equipped with 2 tools: the \texttt{Terminal} tool that allows execution of bash commands like \texttt{rg} (ripgrep), \texttt{find}, \texttt{ls}, \texttt{grep}, and the \texttt{LocalizationFinish} tool to submit the predicted files, modules, and functions after completing the localization. To support faster execution of grep-like commands, we additionally ensure that ripgrep~\footnote{https://github.com/BurntSushi/ripgrep} is installed in the agent's environment.
\sonicomment{TODO: add prompts and tool definitions in appendix}

\subsection{Reward Design}\label{sec:reward_design}

% Next, we describe the design of the reward function used during reinforcement learning experiments.

For each multi-turn trajectory/rollout $\tau$ sampled from the LLM agent, we extract the prediction $y$ from the \texttt{LocalizationFinish} tool which consists of relevant files, modules and functions predicted by the agent. Our core rewards comprise of F1 scores for different granularities: $r^{\mathsf{f1-file}} \in [0,1]$ (File-level F1), $r^{\mathsf{f1-module}} \in [0, 1]$ (Module-level F1), and $r^{\mathsf{f1-func}} \in [0, 1]$ (Function-level F1). During our initial training experiments, we observe that without explicitly controlling the maximum number of turns, model training can eventually crash due to constantly reaching maximum number of turns where rollouts will always be assigned a zero reward due to the trajectory being incomplete. To alleviate this, we explicitly reward the model if and only if the rollout completed in exactly $k$ turns, $r^{\mathsf{turn}} \in \{0,1\}$. We find that this simple intervention is enough to make \methodname to consistently generate a prediction within the step-limit. Overall, our reward function is a summation of all these rewards.
\begin{align}
    r(\tau, y, y^{\star}) &= r^{\mathsf{f1-file}}(y, y^{\star}) + r^{\mathsf{f1-module}}(y, y^{\star}) \nonumber \\ &+ r^{\mathsf{f1-func}}
    (y, y^{\star})
    \nonumber \\ &+ r^{\mathsf{turn}}(\tau, k)
\end{align}
% \lscomment{let's write everything first then cut what we need to maintain page limit. There's not much urgency to put anything in the appendix right now --> ok}
% \sonicomment{Can we shift this to appendix? Enhancing parallel tool-calling is not the primary objective of our paper.}
We also experimented with auxiliary rewards to enhance \methodname such as explicitly rewarding parallel tool-calling and found this to be harmful for model performance.

\subsection{Learning Algorithm}\label{sec:train_algo}

To implement our training backend, we leverage SkyRL~\cite{griggs2025skrylv01}. SkyRL is a modular framework for training language models with RL which supports crucial features such as asynchronous RL training where both weight optimization and rollout generation can occur in parallel that allows for better GPU utilization. In doing this, weight updates occur when there are sufficiently enough rollouts which maybe potentially sampled from an the model checkpoint a few steps back i.e $n^{th}$ training step may include trajectories sampled the model from the $(n-t)^{th}$ step, where $t$ is called the maximum staleness (set to 4). After the weight updates complete for a training step, the model weights are updated in the vLLM engine and any ongoing inferences are aborted.

For training, we use Group Sequence Policy Optimization (GSPO)~\cite{zheng2025groupsequencepolicyoptimization}. The loss is expressed as:
\begin{align}
    \mathcal{J}_{\text{GSPO}}(\theta) &= \nonumber \\  \mathbb{E}_i &\left[ \frac{1}{G} \sum_{i=1}^{G} \min\left( s_i(\theta) \hat{A}_i,\, \text{clip}\left( s_i(\theta), \varepsilon \right) \hat{A}_i \right) \right]
    % \\
    % \nonumber \\
    % \hat{A}_i &= r_i - \text{mean}(\mathbf{r}), \mathbf{r} = \{r_0, ..., r_N\}
    % \label{eq:gspo}
\end{align}
where $s_i$ is the importance ratio derived from sequence likelihood~\cite{zheng-etal-2023-click}:
\begin{align}
    s_i(\theta) = \exp\left( \frac{1}{|y_i|} \sum_{t=1}^{|y_i|} \log \frac{\pi_\theta(y_{i,t} | x, y_{i,<t})}{\pi_{\theta_{\text{old}}}(y_{i,t} | x, y_{i,<t})} \right)
    \label{eq:is}
\end{align}
Following DR. GRPO~\cite{liu2025understandingr1zeroliketrainingcritical}, we remove KL regularization term from the loss function and the standard deviation from the advantage calculation.
\begin{align}
    \hat{A}_i = r_i - \text{mean}(\mathbf{r}), \mathbf{r} = \{r_0, ..., r_N\}
\end{align}
In preliminary experiments, we found GRPO~\cite{shao2024deepseekmathpushinglimitsmathematical} is prone to failure later in training. We experience hardware issues (appendix)

% \subsection{Implementation}



% All submissions must follow the specified format.

% On-Policy Distillation we'll add here. 